Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2023-03-18 beap_pres_dec2022/beap_pres_dec.tex
some bus presentation updates

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{poyglut.png}
		\end{center} \pause

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{direpeat.png}
		\end{center} \pause

		\begin{alertblock}{Tandem Repeats}
			Sequence of residues which are repeated a number of times
		\end{alertblock}

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{tandem.png}
			\includegraphics[width=5cm, height=1cm]{tandem.png}
		\end{center}

@@

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and their Evolution? }

@@

	\begin{frame}{What will this Study Explore?}
		\begin{itemize}
			\item Estimation of evolutionary parameters (mutation rate, indel rates) \newline
			\item Various models of insertions and deletions \newline
			\item Summary statistics which best explain data
		\end{itemize}

@@

	%Slide 12 - Here put the ABC-MCMC algorithm described by Marjoram (one Brian used in his MCMC slides)
	\begin{frame}{MCMC for ABC}

>>>>

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{poyglut.png}
		\end{center}

@@

		\begin{center}
			\includegraphics[width=5cm, height=1cm]{direpeat.png}
		\end{center}

		\begin{alertblock}{Imperfect Repeats}
			Regions in which the repeat units are not the same
		\end{alertblock}

		\begin{center}
			\includegraphics[width=6cm, height=1.2cm]{imperfect.png}
		\end{center}

@@

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and their Evolution?}

@@

	\begin{frame}{What Did we Do in this Study?}
		\begin{itemize}
			\item Programmed an ABC-MCMC using \texttt{C++} which consisted of a simulation step where amino acid sequences were altered by point mutations and insertions/deletions \newline
			\item Utilized the exponential distribution with ($\beta$ = length*indel\_rate) to see if the length of a repeat plays a role in its mutation \newline
			\item Attempted to estimate evolutionary parameters such as mutation rates and insertion/deletion rates \newline
			\item Explored summary statistics that could quantitatively explain characteristics of LCRs

@@

	%Slide 12 - Here put the ABC-MCMC algorithm described by Marjoram (one Brian used in his MCMC slides)
	%%% SO HERE WE NEED TO RE-EVALUATE THE SLIDES - March 18 2023
	\begin{frame}{MCMC for ABC}
